% Most idea comes from this SE answer
% https://tex.stackexchange.com/a/59933/81126
% Also inspired by Dr. Joe Kirtland's LaTeX recommendation
%
% Significantly changed by Pablo Rivas in 2018
% > If you like this, buy me a Dr. Pepper or Cofe (black, medium or dark roast)
%
% This is to provide a LaTeX-based template for a letter that follows Marist's
% official publishing guidlines.
%
% Letter.tex
% This file is the one that you will edit more often. This is where you will
% specify your recipient and the main body of your letter. If you have not
% done so, you should have your information filled-in in MaristLetterDefs.tex
% in the first few lines.


\documentclass{article}

\usepackage{lipsum}

% Recipient info goes here
\providecommand\Maristtoname{Hiring Committee}
\providecommand\Maristtoaddress{Division of Artificial Intelligence\\
                                Facebook Inc. \\
                                New York, NY \ \ 17901\\
                                USA}

% Date (defaults to today)
\providecommand\Maristdate{\today}
% Subject line, if any
\providecommand\Maristsubject{\textbf{RE: Recommendation letter for Mary Marist}}
% Opening and closing, (I was taught to use commas but you can remove them here)
\providecommand\Maristopening{Dear \Maristtoname,}
\providecommand\Maristclosing{Sincerely,}

\input{MaristLetterDefs}

\begin{document}
It is a privilege for me to write this recommendation in favor of Miss Mary
Marist who is a student of mine at the Computer Science Department. I have been
fortunate of having her as a student already. During the time she was in my
class she demonstrated interest and participated frequently, always 
engaged and fully present.

I have known her for almost three years and I can testify about her devotion to
computer science and her leadership skills. The programming assignments she has
turned in have high quality and many times they surpass my expectations. She
has been dedicated to my class and has asked the right questions.

My desire is for you to consider her application as a software engineer for the
following reasons:
\begin{itemize}
  \item she is very smart
  \item she is cool
  \item bullet points are cool
\end{itemize}

Please let me know if you wish to receive more information about her, or
samples of her best programming projects from my class of Software Development.
Feel free to contact me for any questions you may have about her.

Thank you for your time.
\end{document}
